---
title: "TASK"
output: html_notebook
---

# load the package
```{r}
library(AICcmodavg) 
```

#load the beetle dataset 
```{r}
data("beetle")  
```

#display the bettle dataset
```{r}
beetle
```
```{r}
library(ggplot2)
```

#Plot a line graph for the variables Number_tested vs Number_killed against Dose.
```{r}
In <- ggplot(data = beetle,
             aes(x = Mortality_rate,
                 y = Dose,
                 ))+
  geom_line()
In
```

#Write an R program to create three vectors a, b, c with 5 integers. Combine the three vectors to become a 3×5 matrix where each column represents a vector. Print the content of the matrix. Plot a graph and label correctly.
```{r}
a = c(0.5, 10,0.3,12.4,9.5)
b = c(2.0,1.0,4.0,4.9,5.0)
c = c(3.0,3,0.5,6.0,0.9)
#combine the vectors and create a dataframe.
z_bind <-as.data.frame(cbind(a,b,c))
```

```{r}
z_bind
```


```{r}
mean(a)

```


```{r}

plot(a,b, type = "l")
hist(a,probability = T, add = T)
```

#
```{r}
p<-ggplot()+
  layer(data = z_bind,
        stat = "identity",
        geom = "line",
        mapping = aes(x = a, y = b, colour = c),
        position = "identity")
plot(p)
```
#Write a R program to create a Data frames which contain details of 5 employees and display the details.  (Name, Age, Role and Length of service)
```{r}
Name = c("Jo", "James","Ahmed","Buhari","Abbas")
Age = c(23,39,40,21,26)
Role = c("Manager","HR","technician","pilot","bursar")
L_S =c(12,32,20,10,5)

Details_employees =as.data.frame(cbind(Name,Age,Role,L_S))

```

```{r}
Details_employees
```
#Import the GGPLOT 2 library and plot a graph using the qplotfunction.  X axis is the sequence of 1:20 and the y axis is the x ^ 2.  Label the graph appropriately. install.packages("ggplot2", dependencies = TRUE
```{r}
library(ggplot2)
```

```{r}
x = seq(1:20)
y = x ^ 2

c = as.data.frame(cbind(x,y))
```

```{r}
qplot(x,y, data = c,
      geom = "line")
```

```{r}
f = function(){
  a = seq(1:20)
  b = a ^ 2
  qplot(a,b)
}
f()
```
# Create a simple bar plot of five subjects
```{r}
scores = c(20,30,40,80,100)
barplot(scores,
        ylab = "Scores",
        xlab = "Subjects",
        names.arg = c("MAths", "Eng.","Chem.","Phy.","Bio."),
        col = "Blue")
```

#Write a R program to take input from the user (name and age) and display the values. 
```{r}
name = readline("What is your name:")
age = readline("how old are you:")
print(paste("Hey" ,name,"are you", age, "?"))
```


```{r}

```


#Write a R program to create a sequence of numbers from 20 to 50 and find the mean of numbers from 20 to 50 and sum of numbers.
```{r}
d = seq(20:50)
mean(d)
sum(d)
```
#Write a R program to create a vector which contains 10 random integer values between -50 and +50
```{r}
random_integer <- cbind(runif(10,  -50, 50))#runif()refers to random uniform.
random_integer
```
#Write a R program to get the first 10 Fibonacci numbers.
```{r}
nterm <- as.integer(readline(prompt = "Number of terms:"))
n1 = 0
n2 = 1
count = 2
if (nterm <= 0){
  print("Choose a positive number")
} else{
if (nterm == 1){
print("Fibonacci sequence:")
print(n1)
} else {
print("fibonacci sequence:")
print(n1)
print(n2)
while (count < nterm){
nth = n1 + n2
print(nth)
n1 = n2
n2 = nth
count = count + 1
}
        
} 
}
```
#Write a R program to print the numbers from 1 to 100 and print "Fizz" for multiples of 3, print "Buzz" for multiples of 5, and print "FizzBuzz" for multiples of both.

```{r}
for (i in 1:100){
  if (i %% 3 == 0 & i %% 5 == 0)
    print("FizzBuzz")

  } else if (i %% 3 == 0) {
  print("Fizz")

  } else if (i %% 5 == 0) {
  print("Buzz")
  } else {
  print(i)
}
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
